---
title: "Vignette: genevoisgame"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{trust_games}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package is designed to allow simulation of a non-cooperative game theoretic model that evaluates whether or not two parties will agree to sign a treaty over a shared transboundary aquifer. The model incorporates geophysical, economic, and social features of the transboundary scenario to make this determination. These include aquifer connectivity and drawdown, the cost of abstracting groundwater and potential alternative sources, and trust between the players.

## Background 

The game is based on the Genevois aquifer, shared by Switzerland and France, where an important and influential groundwater sharing treaty has existed since the 1970s. Thus, in the game, the two players are refered to S and F representing these two countries.

Utilities for Switzerland and France are given by:
$$U_i(q_s,q_f)=-p_{0i}(Q_i-q_i)-\beta (d_{Bi}-h_i) q_i - c_{0rs} - c_{ri}r_M(\Omega)-\epsilon_i(\Omega)\pm z$$
where $q_i$ is the water abstracted by country $i$, $p_{0i}$ is the unit cost of water from some alternative water source, $Q_i$ is the total water requirement, $d_{Bi}-h_i$ is the groundwater depth (calculated as the depth to the bottom of the aquifer, $d_{Bi}$, minus hydraulic thickness of the water table, $h_i$), $\beta$ is the volumetric pumping cost per groundwater depth, $c_{0rs}$ is a fixed cost for building the recharge facility, $c_{ri}$ is the unit cost of recharge (because France doesn't pay directly, $c_{0rf}=c_{rf}=0$), $r_M(\Omega)$ is managed aquifer recharge and is high (low) if $\Omega=1$ ($\Omega=0$), $\epsilon_i$ accounts for uncertain costs of signing the treaty and is zero in the case of no treaty, and $z$ is the price paid by France to Switzerland for French abstraction per the agreement. Because recharge is limited by physical properties of water supply and the aquifer, we assume that the construction of a recharge facility entails a fixed quantity of recharge, $r_M$.
The hydraulic thickness of the water table is the hydraulic head relative to the bottom of the aquifer. In confined aquifers, the hydraulic thickness is greater than the aquifer thickness and changes linearly with pumping. It is given by
$$ h_i=h_{0i}-D_{ii} q_i-D_{ij} q_j+D_{ir}(\Omega) r_M(\Omega),$$
where $h_{0i}$ is the natural thickness of the water table accounting for steady-state recharge and discharge, and the remaining coefficients capture aquifer properties that relate groundwater depth with abstraction within country $i$ ($D_{ii}$), abstraction by country $j$ ($D_{ij}$), and managed recharge ($D_{ir}$). 

For unconfined aquifers, abstraction is related linearly with discharge potential, $\phi_i$, which is equivalent to the square of the thickness of the water table, which is given by
$$h_i^2=\phi_i=h_{0i}^2-\Phi_{ii}q_i-\Phi_{ij}q_j+\Phi_{ir}(\Omega)r_M(\Omega),$$
where the coefficients relate discharge potential with abstraction by country $i$ ($\Phi_{ii}$), abstraction by country $j$ ($\Phi_{ij}$), and managed recharge ($\Phi_{ir}$). 

## Confined aquifer: trust vs trust

This vignette will show you the basic utilization of the package. If you haven't installed the `genevoisgame` package, you can do so using `devtools::install_github`:

```{r eval=FALSE}
# Install the package
devtools::install_github("https://github.com/gopalpenny/genevoisgame")
```

Next we will load the package along with some of the `tidyverse` packages for easy data wrangling.

```{r setup, message=FALSE}
library(genevoisgame)
library(dplyr)
library(tidyr)
library(ggplot2)
```

We will use the built-in dataset `example_params_confined` as a basis for our analysis. Whenever a treaty game is simulated, parameters are validated using the `check_params` function, and a full list of required parameters can be found in the documentation for this function. The game determines whether to use a confined or unconfined scenario using the parameters input to the game. If `Dxx` are used, the game will apply to a *confined* aquifer. If `PHIxx` are used, the game will apply to an *unconfined* aquifer. See `?check_params` for details.

The game is evaluated using `evaluate_treaty` for a single scenario, or can be evaluated for multiple scenarios using `evaluate_treaty_cases`. For confined aquifers, the game is analyzed using analytical equations.

In order to plot contour lines of the outcomes, we will use the function `get_contours`, which is part of the `genevoisgame` package.

```{r confined_example,fig.width=5,fig.height=3}
# Generate parameter data.frame
params_basic_trust_v_trust <- example_params_confined %>% select(-gf,-gs)
params_df_trust_v_trust <- params_basic_trust_v_trust %>% 
  crossing(gs=seq(0,1,by=.05),
           gf=seq(0,1,by=.05))

# Run the game theoretic model
outcomes_trust_v_trust <- evaluate_treaty_cases(params_df_trust_v_trust,"pqud")

# Get contours for the model
cl_trust_v_trust <- get_contours(outcomes_trust_v_trust %>% rename(x=gs,y=gf,z=zRange),
                                 levels=c(-0.2,0,0.2))

# Plot the output
ggplot() + 
  geom_raster(data=outcomes_trust_v_trust,aes(gs,gf,fill=zRange)) +
  geom_path(data=cl_trust_v_trust,aes(x,y,group=line,linetype=level_factor)) +
  scale_fill_gradient2() + coord_equal() +
  theme(legend.box = "horizontal")
```

Note that the parameters `"pqud"` in the `evaluate_treaty_cases` function returns utility (u), depth (d), pumping (q), and the varying parameters (p). Checking the names of the output `outcomes_trust_v_trust`, we can see the these values are present for the potential scenarios first best (\*hat), nash equilibrium (\*star), cheating the other player (\*double), victim of the cheat (\*hat_double), and cheating by both players (\*double_double). The nash equilibrium is the scenario without a treaty. The others involve the signing of a treaty and the combination of players being gentleman or cheats.

```{r}
names(outcomes_trust_v_trust)
```

Sometimes it may be valuable to plot the depth, utility, and pumping output along some axis. There is a helper function, `gather_outcomes` which can help with this. It gathers the output variables in long format so that it can be plotted against another variable. In this case, we are interested in seeing how the outcomes vary over `gs`, holding `gf` constant at 0.5.

```{r}
outcomes_trust_long <- outcomes_trust_v_trust %>% filter(gf==0.5) %>% gather_outcomes()
```

Using `facet_wrap` from `ggplot2` and careful selection of linetypes and colors, we can better see the effect of `gs` on the outcome variables under scenarios of a treaty ("hat"), nash equlibrium ("star"), cheat ("double"), and victim ("hat_double").

```{r fig.width=5,fig.height=4.5}
ggplot(outcomes_trust_long) +
  geom_line(aes(x=gs,y=val,color=country,linetype=variable_subcat)) +
  facet_wrap(~variable_cat,scales="free_y",ncol=1) +
  scale_linetype_manual(values=c("solid","dashed","dotted","longdash","dotdash")) +
  theme(legend.key.width = unit(1,"cm"))
```

## Unconfined aquifer: trust vs trust

We will now do the same analysis, but using `example_params_unconfined`, meaning that the game will operate on an unconfined aquifer.

For unconfined aquifers, the underlying game equations are nonlinear and the results are calculated numerically using the `multiroot` function from the `rootSolve` package. For this reason, game simulation takes longer for unconfined aquifers. Also note that the results for `zRange` are rounded to the 6th decimal place to avoid numerical errors in determination of the treaty.

```{r unconfined_example,fig.width=5,fig.height=3}
params_basic_trust_v_trust_un <- example_params_unconfined %>% select(-gf,-gs)
params_df_trust_v_trust_un <- params_basic_trust_v_trust_un %>% 
  crossing(gs=seq(0,1,by=.2),
           gf=seq(0,1,by=.2))


# Run the game theoretic model
outcomes_trust_v_trust_un <- evaluate_treaty_cases(params_df_trust_v_trust_un)

# Get contours for the model
cl_trust_v_trust_un <- get_contours(outcomes_trust_v_trust_un %>% rename(x=gs,y=gf,z=zRange),
                                    levels=c(-0.1,-0.05,0,0.05,0.1))

# Plot the output
ggplot() + 
  geom_raster(data=outcomes_trust_v_trust_un,aes(gs,gf,fill=zRange)) +
  geom_path(data=cl_trust_v_trust_un,aes(x,y,group=line,linetype=level_factor)) +
  scale_fill_gradient2() + coord_equal() +
  theme(legend.box = "horizontal")
```

```{r echo=FALSE}

# Generate parameter data.frame
# params_get(scenario) %>% %>% select(-Dss,-Dff,-Dsf,-Dfs) %>%
#   mutate(rmN=8,gs=0.4,gf=0.4)
# params_df <- params_basic %>% 
#   crossing(nesting(Dss=seq(0.5,5,by=.5),
#                    Dff=seq(0.5,5,by=.5)),
#            nesting(Dsf=seq(0.5,5,by=.5),
#                    Dfs=seq(0.5,5,by=.5)))
# params_df_trust_v_Dij_over_Dii <- params_basic_trust_v_Dij_over_Dii %>% 
#   crossing(nesting(Dij_over_Dii=seq(0.05,0.95,by=0.05)),
#            nesting(gs=seq(.01,1,by=.05),
#                    gf=seq(.01,1,by=.05))) %>% 
#   mutate(Dss=Dsf/Dij_over_Dii,Dff=Dfs/Dij_over_Dii)
```

