---
title: "genevese_game"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{genevese_game}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


de los Cobos 2018: "The company could exploit all the existing pumping wells (100,000 m3/day)
and not have to build a new plant for treating lake water (100 million Swiss francs)
that would only be used for a few weeks of the year."

de los Cobos 2018: "The artificial recharge fee per cubic metre of water extracted could be less than
0.07 Swiss francs when the annual volume of water pumped was in excess of 20 million m3.
However, the fee could rise to 0.12 Swiss francs or more if the volume of water pumped was
less than 10 million m3."


de los Cobos, 2018: "The cost of a new water treatment plant in the lake, with the necessary modifications
to the water supply system, was approximately 150 million Swiss francs (as at 1975). The
cost of a groundwater aquifer recharge (MAR) system. including an automatic laboratory
system for pollution detection in the Arve River, was around 20 million Swiss francs."

NOTES: x_var and y_var are only for plotting and get_roots.
          The first in the list are the plotting variables. After that, the remaining y_var must be equal and are numerically solved in get_roots
       xl and yl are the axis labels, but are not associated with x_var and y_var -- must be done manually
       when running the code, can use additional variables as desired.
       simply place them in first position of x_var and y_var


```{r setup}
library(aquiferXgame)
```
